\textbf{Dynamic Hover Detection:\\Creating GUIs in Elm}

### 2014-01-01 paper/paper.tex
More revisions on hoverables

The first parameter to
\texttt{hoverables} denotes the initial value of the \texttt{events} signal
(signals in Elm must always be defined).
The \texttt{hoverable} part of the record takes an element and attaches hover
detection to it. Whenever the mouse hovers (or stops hovering) over the
element, an event is fired on the \texttt{events} signal. The value of that
event is determined by the \texttt{(Bool -> a)} parameter of the
\texttt{hoverable} function. In many cases, this will be \texttt{id} so that the
\texttt{events} signal is \texttt{True} when the element is being hovered upon
and \texttt{False} when it is not. However, the \texttt{(Bool -> a)} parameter
allows you to provide a different value on the \texttt{events} signal for different elements.

@@

There is a subtle, yet very important difference between \texttt{hoverables} and
\texttt{hoverable}. After providing the initial parameter to
\texttt{hoverables}, you are given a signal and a way to attach elements to that
signal. By applying the \texttt{hoverable} part of the record to multiple
elements, we can create a single signal which responds to the hover information
of those elements, instead of one signal per element. We can then exploit this
property to detect hoverable information on a signal of elements. As the value
of the input signal of elements changes, we attach the hover information to the
new element without having to create a new output signal.

@@

Notice that \texttt{pool.hoverable} is partially applied to \texttt{id}
purely, and then lifted on to the argument.

>>>>

The first parameter to \texttt{hoverables} denotes the initial value of the
\texttt{events} signal (signals in Elm must always be defined). The record's
\texttt{hoverable} function is applied to an element and attaches hover
detection to it. Whenever the mouse hovers (or stops hovering) over the element,
an event is fired on the \texttt{events} signal. The value of that event is
determined by the \texttt{(Bool -> a)} parameter of the \texttt{hoverable}
function. In many cases, \texttt{a} will be \texttt{Bool} and the function will
be \texttt{id}. In general, the record's \texttt{hoverable} may be applied
multiple times with all elements it produces reporting their hover information
on \texttt{events}. In this case, \texttt{a} can serve as an identifier, and is
provided by the function argument.

@@

Using only \texttt{hoverable}, we are restricted to one element per signal. With
\texttt{hoverables}, the hover information of an element can be added to an
existing signal, and can even be added during program execution, that is, when
the element is a signal. As the value of a signal of elements changes, we attach
the hover information to the each new element without having to create a new
output signal. We do this by partially applying \texttt{pool.hoverable} to
\texttt{id} purely, and then lifting it on to the argument.

@@
